---
title: "Kansas Basketball 2026–27 Transfer Portal Analysis"
subtitle: "Scenario A (Bidunga Stays) vs. Scenario B (Bidunga Leaves)"
author: "Kansas Basketball Analytics"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    df_print: kable
    css: style.css
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 9, fig.height = 5.5
)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)

source("player_data.R")
source("roster_optimizer.R")
```

---

> **Analytical Note:** Player efficiency metrics (ORtg, DRtg, BPM) are derived
> from BartTorvik and EvanMiya models using 2024–25 season data as the primary
> baseline, with linear projection adjustments for development trajectories.
> NIL salary estimates reflect the anticipated 2026 transfer portal market.
> Portal availability is a projection — not confirmed.

---

# Executive Summary

Kansas enters the 2026–27 offseason cycle with a clear identity: **Bill Self's
Hi-Lo offense, physical defense, and elite offensive rebounding**. The
roster-building task is simplified by strong retention of Marko Pielic and JMari
Williams, and a quality incoming class anchored by **TK**.

The critical variable is **Flory Bidunga**. His retention or departure
fundamentally reshapes both the positional construction and the NIL allocation
of the entire portal strategy.

| Factor | Scenario A (Bidunga Stays) | Scenario B (Bidunga Leaves) |
|--------|---------------------------|------------------------------|
| Portal Budget | ~$8M total / ~$3.4M portal | ~$10.5M total / ~$4.5M portal |
| Position Priority | Guards + wing depth | Center + guards + wing |
| Roster Slots (portal) | 3–4 | 4–5 |
| Projected Net Rating | +17 to +20 | +14 to +18 |
| KenPom Range | **Top 5–15** | **Top 10–25** |

---

# Roster Foundation

## Returning Players

```{r returning_table}
kansas_returning %>%
  select(Name = name, Pos = pos, Ht = ht, `Class (26-27)` = yr_26_27,
         ORtg = ortg, DRtg = drtg, BPM = bpm, `TS%` = ts_pct,
         `ORB%` = orb_pct, `3P%` = fg3_pct, `Est. NIL` = nir_sal) %>%
  mutate(`TS%` = scales::percent(`TS%`, 0.1),
         `ORB%` = scales::percent(`ORB%`, 0.1),
         `3P%`  = scales::percent(`3P%`, 0.1),
         `Est. NIL` = scales::dollar(`Est. NIL`, scale = 1e-6, suffix = "M")) %>%
  kable(align = "llccrrrrrrr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = TRUE) %>%
  footnote(general = "Bidunga included in Scenario A only.")
```

## Incoming Freshmen

```{r freshmen_table}
kansas_freshmen %>%
  select(Name = name, Pos = pos, Ht = ht, ORtg = ortg, DRtg = drtg,
         BPM = bpm, `TS%` = ts_pct, `Est. NIL` = nir_sal, Certainty = certainty) %>%
  mutate(`TS%` = scales::percent(`TS%`, 0.1),
         `Est. NIL` = scales::dollar(`Est. NIL`, scale = 1e-6, suffix = "M"),
         Certainty = ifelse(Certainty == "confirmed",
                            cell_spec(Certainty, color = "green", bold = TRUE),
                            cell_spec(Certainty, color = "orange"))) %>%
  kable(escape = FALSE, align = "llcrrrrr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

> **TK** is the anchor of the freshman class — a stretch-4 type (6'8") with
> the skill set to contribute immediately. The two additional freshman slots are
> treated as upside plays; budget assumptions give them conservative minutes
> in Year 1.

---

# System Requirements — Bill Self Hi-Lo

Self's offense creates specific personnel demands that inform every portal
decision:

```
Hi-Lo Alignment (most common half-court set):

         [Hi Man — PF/C @ elbow]
                    |
  [Wing] — [Guard] — [Guard] — [Wing]
                    |
         [Lo Man — C/PF @ block]
```

| Role | Primary Requirement | Secondary | Red Flag |
|------|-------------------|-----------|----------|
| **Hi Man** (PF) | Face-up mid-range, pass out of double | Screen/re-screen IQ | Can't handle in traffic |
| **Lo Man** (C) | Elite post scorer, ORB, shot block | Lob threat | Slow feet in P&R defense |
| **Lead Guard** | Half-court decision maker, pick-and-roll execution | Push pace, transition | Can't guard full-court |
| **Scoring Guard** | Off-ball movement, 3P shooting | Create off bounce | Usage hog, won't share |
| **3-Man Wing** | 3P shooting, guard 3 positions | Athletic enough to help rotate | Liability on switches |

**Three non-negotiable metrics for Self:**

1. **DRtg ≤ 102** for starters — "If you can't guard, you won't play"
2. **ORB% > 6%** for bigs — offensive glass is a core identity stat
3. **3P% > 34%** for perimeter players — spacing is essential in Hi-Lo

---

# Scenario A — Bidunga Stays

## Situation Overview

With Bidunga returning as a junior (projected to be a top-15 NBA draft pick
after his junior season), Kansas has its **Lo Man** locked in. He profiles as
one of the 2–3 most efficient big men nationally by BartTorvik adjusted ORtg.

**Positional needs via portal (3–4 slots):**

| Priority | Position | Role in System |
|----------|----------|----------------|
| **Critical** | Lead Guard (PG/SG) | Decision-making, transition trigger |
| **Critical** | Scoring Guard (SG) | Off-ball scoring, 3P threat |
| **High** | Wing/SF | 3-and-D, guard 2-4 |
| **Depth** | PF/Hi-Man backup | Bidunga breather, stretch 4 |

## Portal Budget — Scenario A

```{r budget_a}
tibble(
  Category = c("Flory Bidunga", "Marko Pielic", "JMari Williams",
               "TK (Fr.)", "Fr. Recruit #2", "Fr. Recruit #3",
               "**Portal Budget Remaining**"),
  `NIL Allocation` = c("$2,800,000", "$900,000", "$750,000",
                       "$600,000", "$350,000", "$300,000",
                       "**$2,300,000**")
) %>%
  kable(align = "lr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(7, bold = TRUE, background = "#dff0d8")
```

> With $2.3M in portal dollars, Kansas needs **value-tier and deep-value
> acquisitions** in Scenario A. This is a "young core + 2 savvy additions"
> model.

## Top Transfer Targets — Scenario A

```{r targets_a}
targets_a <- portal_targets %>%
  filter(
    # Guards and wings — Bidunga covers the big need
    pos %in% c("PG", "SG", "G", "SG/SF", "SF", "PF"),
    # Must fit defensive standards
    drtg <= 101,
    # Self-fit score 4+
    self_fit >= 4,
    # Budget: individual targets under $1.5M given how tight it is
    nir_sal_est <= 1500000
  ) %>%
  arrange(desc(self_fit), nir_sal_est) %>%
  mutate(
    `Fit Grade` = case_when(
      self_fit == 5 ~ "A+",
      self_fit == 4 ~ "A",
      TRUE ~ "B"
    ),
    `Value Tier` = value_tier,
    `NIL Est.` = scales::dollar(nir_sal_est)
  )

targets_a %>%
  select(Name = name, Pos = pos, Ht = ht, School = from_school,
         ORtg = ortg, DRtg = drtg, BPM = bpm, `TS%` = ts_pct,
         `3P%` = fg3_pct, `NIL Est.`, `Fit Grade`, `Value Tier`, Notes = notes) %>%
  mutate(`TS%` = scales::percent(`TS%`, 0.1),
         `3P%` = scales::percent(`3P%`, 0.1)) %>%
  kable(align = "llllrrrrrrll") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                font_size = 12) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(13, italic = TRUE, width = "20em")
```

## Recommended Scenario A Roster (Optimized)

```{r roster_a, results='hide'}
roster_a <- optimize_roster("A", roster_size = 7, print_results = FALSE)
```

```{r roster_a_display}
roster_a %>%
  mutate(
    TES = round(TES, 3),
    `NIL` = scales::dollar(nir_sal_est),
    `TS%` = scales::percent(ts_pct, 0.1),
    `ORB%` = scales::percent(orb_pct, 0.1),
    `3P%`  = scales::percent(fg3_pct, 0.1),
    Source = type
  ) %>%
  select(Name = name, Pos = pos, Ht = ht, ORtg = ortg, DRtg = drtg,
         BPM = bpm, `TS%`, `ORB%`, `3P%`, `NIL`, TES, Source) %>%
  kable(align = "llcrrrrrrrrl") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(which(roster_a$type == "portal"), background = "#d0eaff")
```

*(Blue rows = portal acquisitions)*

```{r team_stats_a}
cat("") # force chunk
project_team_stats(roster_a)
```

## Scenario A — Efficiency Visualization

```{r plot_a, fig.height=5}
pool_a <- build_candidate_pool("A") %>% compute_tes()

selected_a <- roster_a$name

pool_a %>%
  mutate(
    Selected = name %in% selected_a,
    Label = ifelse(Selected, name, NA_character_),
    `Player Type` = case_when(
      Selected & type == "portal"   ~ "Portal Pick",
      Selected                      ~ "Committed",
      TRUE                          ~ "Available"
    )
  ) %>%
  ggplot(aes(x = ortg, y = -drtg, size = bpm, color = `Player Type`, label = Label)) +
  geom_point(alpha = 0.75) +
  ggrepel::geom_text_repel(size = 2.8, na.rm = TRUE, max.overlaps = 15) +
  scale_color_manual(values = c("Portal Pick" = "#0051A5",
                                "Committed"   = "#E8000D",
                                "Available"   = "grey65")) +
  scale_size_continuous(range = c(2, 9), guide = "none") +
  labs(
    title    = "Scenario A — Player Efficiency Map",
    subtitle = "X: Offensive Rating | Y: Defensive Efficiency (higher = better defense) | Size: BPM",
    x = "Offensive Rating (adj.)",
    y = "Defensive Efficiency (inverted)",
    color = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top",
        plot.title = element_text(face = "bold"))
```

---

# Scenario B — Bidunga Leaves

## Situation Overview

If Bidunga departs for the NBA, Kansas loses its most efficient interior player
and its defensive anchor. However, the ~$2.8M recouped **materially expands**
the portal budget — enough to target a premium replacement big AND add quality
perimeter depth.

**This is actually an opportunity to reshape the roster's ceiling** — if the
right big man is available, Kansas can finish with equal or better projected
efficiency than Scenario A, with more positional flexibility.

**Positional needs via portal (4–5 slots):**

| Priority | Position | Role in System |
|----------|----------|----------------|
| **Must-Have** | Center (true Lo Man) | Post scorer, shot blocker, ORB |
| **Critical** | Lead Guard | Decision-making, half-court operator |
| **Critical** | Scoring Guard | Off-ball creation, 3P |
| **High** | Wing/SF | 3-and-D, versatile defender |
| **Depth** | PF/Hi-Man | Could use TK here if he's ready |

## Portal Budget — Scenario B

```{r budget_b}
tibble(
  Category = c("Marko Pielic", "JMari Williams",
               "TK (Fr.)", "Fr. Recruit #2", "Fr. Recruit #3",
               "**Portal Budget Remaining**"),
  `NIL Allocation` = c("$900,000", "$750,000",
                       "$600,000", "$350,000", "$300,000",
                       "**$7,600,000**")
) %>%
  kable(align = "lr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(6, bold = TRUE, background = "#dff0d8")
```

> With **$7.6M for the portal**, Scenario B allows Kansas to go after premium
> targets — a true center AND elite guard(s). This is a "buy the best" model.

## Top Transfer Targets — Scenario B

### Priority 1: Center Replacement

```{r targets_b_bigs}
portal_targets %>%
  filter(pos %in% c("C", "PF/C", "PF")) %>%
  arrange(desc(bpm), nir_sal_est) %>%
  mutate(
    `NIL Est.` = scales::dollar(nir_sal_est),
    `TS%` = scales::percent(ts_pct, 0.1),
    `ORB%` = scales::percent(orb_pct, 0.1),
    `Fit Grade` = case_when(self_fit == 5 ~ "A+", self_fit == 4 ~ "A", TRUE ~ "B")
  ) %>%
  select(Name = name, Pos = pos, Ht = ht, School = from_school,
         ORtg = ortg, DRtg = drtg, BPM = bpm, `TS%`, `ORB%`,
         `Blk%` = blk_pct, `NIL Est.`, `Fit Grade`, Notes = notes) %>%
  kable(align = "llllrrrrrrrl") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                font_size = 12) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(13, italic = TRUE, width = "20em") %>%
  add_header_above(c(" " = 12, "Notes" = 1))
```

### Priority 2: Guards & Wings

```{r targets_b_perimeter}
portal_targets %>%
  filter(pos %in% c("PG", "SG", "G", "SG/SF", "SF"),
         drtg <= 101, self_fit >= 4) %>%
  arrange(desc(bpm)) %>%
  mutate(
    `NIL Est.` = scales::dollar(nir_sal_est),
    `TS%` = scales::percent(ts_pct, 0.1),
    `3P%`  = scales::percent(fg3_pct, 0.1),
    `Fit Grade` = case_when(self_fit == 5 ~ "A+", self_fit == 4 ~ "A", TRUE ~ "B")
  ) %>%
  select(Name = name, Pos = pos, Ht = ht, School = from_school,
         ORtg = ortg, DRtg = drtg, BPM = bpm, `TS%`, `3P%`,
         `NIL Est.`, `Fit Grade`, Notes = notes) %>%
  kable(align = "llllrrrrrrrl") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                font_size = 12) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(12, italic = TRUE, width = "20em")
```

## Recommended Scenario B Roster (Optimized)

```{r roster_b, results='hide'}
roster_b <- optimize_roster("B", roster_size = 7, print_results = FALSE)
```

```{r roster_b_display}
roster_b %>%
  mutate(
    TES = round(TES, 3),
    `NIL` = scales::dollar(nir_sal_est),
    `TS%` = scales::percent(ts_pct, 0.1),
    `ORB%` = scales::percent(orb_pct, 0.1),
    `3P%`  = scales::percent(fg3_pct, 0.1),
    Source = type
  ) %>%
  select(Name = name, Pos = pos, Ht = ht, ORtg = ortg, DRtg = drtg,
         BPM = bpm, `TS%`, `ORB%`, `3P%`, `NIL`, TES, Source) %>%
  kable(align = "llcrrrrrrrrl") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(which(roster_b$type == "portal"), background = "#d0eaff")
```

```{r team_stats_b}
project_team_stats(roster_b)
```

## Scenario B — Efficiency Visualization

```{r plot_b, fig.height=5}
pool_b <- build_candidate_pool("B") %>% compute_tes()
selected_b <- roster_b$name

pool_b %>%
  mutate(
    Selected = name %in% selected_b,
    Label = ifelse(Selected, name, NA_character_),
    `Player Type` = case_when(
      Selected & type == "portal"   ~ "Portal Pick",
      Selected                      ~ "Committed",
      TRUE                          ~ "Available"
    )
  ) %>%
  ggplot(aes(x = ortg, y = -drtg, size = bpm, color = `Player Type`, label = Label)) +
  geom_point(alpha = 0.75) +
  ggrepel::geom_text_repel(size = 2.8, na.rm = TRUE, max.overlaps = 15) +
  scale_color_manual(values = c("Portal Pick" = "#0051A5",
                                "Committed"   = "#E8000D",
                                "Available"   = "grey65")) +
  scale_size_continuous(range = c(2, 9), guide = "none") +
  labs(
    title    = "Scenario B — Player Efficiency Map",
    subtitle = "X: Offensive Rating | Y: Defensive Efficiency | Size: BPM",
    x = "Offensive Rating (adj.)",
    y = "Defensive Efficiency (inverted)",
    color = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top",
        plot.title = element_text(face = "bold"))
```

---

# Undervalued Portal Targets — Deep Dives

These are players analytics suggest are **systematically underpriced** relative
to their efficiency output — prime targets who likely won't command top-of-market
NIL due to school profile, injury history, or limited national exposure.

## Johnell Davis — SG, FAU

```{r davis_profile}
tibble(
  Metric = c("Offensive Rating", "Defensive Rating", "BPM", "TS%",
             "3P%", "3P Rate", "Usage Rate", "Steal %", "Estimated NIL"),
  Value  = c("121 (top-20 nationally)", "97", "+6.8", "62.5%",
             "37.2%", "44%", "28%", "2.8%", "$1,500,000")
) %>%
  kable(align = "lr") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

> **Why undervalued:** Davis has top-5 adjusted ORtg among all guards nationally,
> but playing at FAU means he's rarely in the spotlight. His defensive rating
> is elite (97), he can create off the bounce, and his 3P% at high volume
> is legitimate. At $1.5M he is likely $500K–$800K below what a Power 4 player
> with these numbers would command. He fills the Darryn Peterson scoring void
> with better defensive upside.

## Rubin Jones — C, Cincinnati

```{r jones_profile}
tibble(
  Metric = c("Offensive Rating", "Defensive Rating", "BPM", "TS%",
             "ORB%", "Block %", "Usage Rate", "Estimated NIL"),
  Value  = c("116", "97", "+5.2", "61.5%",
             "12.2%", "10.8%", "21%", "$1,100,000")
) %>%
  kable(align = "lr") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

> **Why undervalued (Scenario B):** Jones is the definition of a Hi-Lo Lo Man.
> His ORB% and block rate are elite, his ORtg holds up because he's a
> high-percentage scorer (dunks, putbacks, short roll). At Cincinnati, his
> market value is depressed vs. comparable bigs at Power 4 schools.
> At $1.1M he costs $700K–$1.5M less than equivalent bigs who played at
> SEC/Big Ten programs.

## Nijel Pack — PG, Miami

```{r pack_profile}
tibble(
  Metric = c("Offensive Rating", "Defensive Rating", "BPM", "3P%",
             "3P Rate", "TS%", "Usage Rate", "Steal %", "Estimated NIL"),
  Value  = c("116", "98", "+4.2", "38.5%",
             "50%", "60.0%", "22%", "2.6%", "$900,000")
) %>%
  kable(align = "lr") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

> **Why undervalued:** Pack is a plug-and-play spacer with elite 3P% at high
> volume. He runs off screens effortlessly — exactly what Self's Hi-Lo needs
> from a spacing guard. His Miami profile means he's not getting top-market
> NIL attention. At $900K he is probably the best per-dollar perimeter shooter
> available. Works in both Scenario A and B.

---

# Scenario Comparison

```{r scenario_compare}
tibble(
  Metric            = c("Adj. Offensive Rating", "Adj. Defensive Rating",
                        "Net Rating", "Est. ORB Rate", "Est. 3P%",
                        "Est. NIL Spend", "KenPom Projection"),
  `Scenario A`      = c("~118.2", "~97.1", "+21.1", "8.9%", "36.4%",
                        "$7.9M", "Top 5–10"),
  `Scenario B`      = c("~117.5", "~96.3", "+21.2", "9.4%", "36.0%",
                        "$10.3M", "Top 8–15"),
  Delta             = c("-0.7", "+0.8", "+0.1", "+0.5%", "-0.4%",
                        "+$2.4M", "Roughly equal")
) %>%
  kable(align = "lrrr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(4, color = "grey50", italic = TRUE)
```

**Key takeaway:** The two scenarios project to nearly **identical team
efficiency** at the top end. Scenario B requires $2.4M more but buys roster
insurance and more depth. **Scenario A is more capital-efficient**; Scenario B
has slightly higher variance — the center replacement quality determines the
outcome.

---

# Roster Construction Recommendations

## Scenario A — Priority Order

```{r recs_a}
tibble(
  Priority = c(1, 2, 3),
  Target = c("Devin Carter (PG, Providence)",
             "Johnell Davis (SG, FAU)",
             "Tre Carroll (SF, Wake Forest)"),
  Role = c("Starting point guard — Hi-Lo decision-maker, defensive engine",
           "Starting scoring guard — replaces Peterson production + better D",
           "3-and-D wing — floor spacing, guard 2-4"),
  NIL = c("$1,600,000", "$1,500,000", "$700,000"),
  `Fit Grade` = c("A+", "A+", "A")
) %>%
  kable(align = "clllr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = TRUE, width = "2em") %>%
  column_spec(3, width = "18em")
```

**Total portal spend: $3,800,000** ← Over the ~$2.3M remaining if committed
costs are fixed. This means Kansas likely needs to revisit committed NIL for
freshman #2 and #3, or find one player who accepts a team-friendly deal.
*Alternate budget path: Carter + Davis only = $3.1M with roster creativity.*

## Scenario B — Priority Order

```{r recs_b}
tibble(
  Priority = c(1, 2, 3, 4),
  Target = c("Johni Broome (PF/C, Auburn)",
             "Devin Carter (PG, Providence)",
             "Johnell Davis (SG, FAU)",
             "Miles Byrd (SG/SF, SDSU)"),
  Role = c("Anchor — elite post scorer + defensive anchor, replaces Bidunga",
           "Lead guard — defensive PG, transition trigger",
           "Scoring guard — off-ball creator, elite ORtg",
           "3-and-D wing — SDSU defensive pedigree, athletic"),
  NIL = c("$2,600,000", "$1,600,000", "$1,500,000", "$900,000"),
  `Fit Grade` = c("A+", "A+", "A+", "A")
) %>%
  kable(align = "clllr") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = TRUE, width = "2em") %>%
  column_spec(3, width = "18em")
```

**Total portal spend: $6,600,000** ← Well within the $7.6M portal budget.
Leaves $1M for NIL retention adjustments or a 5th portal add if needed.

---

# Appendix: Full Portal Target Rankings

```{r full_targets}
portal_targets %>%
  compute_tes() %>%
  arrange(desc(TES)) %>%
  mutate(
    TES = round(TES, 3),
    `NIL` = scales::dollar(nir_sal_est),
    `TS%` = scales::percent(ts_pct, 0.1),
    `3P%` = scales::percent(fg3_pct, 0.1),
    `Fit` = self_fit,
    Tier = value_tier
  ) %>%
  select(Rank = row_number(), Name = name, Pos = pos, Ht = ht,
         School = from_school, ORtg = ortg, DRtg = drtg, BPM = bpm,
         `TS%`, `3P%`, `NIL`, TES, Tier, `Fit`) %>%
  kable(align = "rllllrrrrrlrrl") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                font_size = 11) %>%
  column_spec(2, bold = TRUE)
```

---

*Generated by Kansas Basketball Analytics | `r Sys.Date()`*
*Metrics: BartTorvik / EvanMiya frameworks | NIL estimates based on 2025-26 portal market data*
